{\itshape Depicting urban boundaries from a mobility network of spatial interactions: A case study of Great Britain with geo-located Twitter data}

### 2016-07-26 urban_boundaries_gb_IJGIS/IJGIS/Paper.tex
Tonight

%\clearpage
\section{Conclusion and Discussion}
In this study, we presented a method to delineate the non-administrative anthropographic urban boundaries in Great Britain using a mobility network of Twitter user spatial interactions, which were inferred from the collective Twitter user movement data extracted from more than 69 million Twitter messages.
In contrast to administrative urban boundaries, our ``bottom-up" approach imposes a virtual fishnet over the islands of Great Britain to partition the space.
To avoid deciding the cell size arbitrarily, we studied the probability distributions of the radius of gyrations of individual Twitters users and selected 10-km as the cell size, which is the distinct geographic distance for separating two main groups of Twitter users in terms of the spatial coverage at the national level.
In addition, this choice allows us to focus on the inter-connections among different urban regions with less attention to movements around a user's neighborhood (i.e., within 10 km radius), such as home or work places.

Supplement Materials section 1

@@

The power of using Twitter user mobility to delineate non-administrative anthropographic boundaries is the ability to redraw the city at different mobility ranges inferred objectively from the collective mobility patterns. 
Urban boundaries redrawn based on Twitter user movement represent physical commutes rather than social ties or phone call initiation to reflect the human interaction space.
This study provides a first step in connecting human mobility research with defining non-administrative anthropographic boundaries, which could assist in resource allocation, political campaigns and urban planning.
However, the geo-located twitter data is not able to generalize to the entire population; therefore, the urban regions that do not have any, or limited, Twitter coverage can be missed during the delineation process.
Yet, our approach is still applicable when more detailed mobility data is available.

>>>>

%\clearpage
\section{Discussion}
However, the geo-located twitter data is not able to generalize to the entire population; therefore, the urban regions that do not have any, or limited, Twitter coverage can be missed during the delineation process.
Yet, our approach is still applicable when more detailed mobility data is available.

\section{Conclusion}
In this study, we presented a method to delineate the non-administrative anthropographic urban boundaries in Great Britain using a mobility network of Twitter user spatial interactions, which were inferred from the collective Twitter user movement data extracted from more than 69 million Twitter messages.
In contrast to administrative urban boundaries, our ``bottom-up" approach imposes a virtual fishnet over the islands of Great Britain to partition the space.
To avoid deciding the cell size arbitrarily, we studied the probability distributions of the radius of gyrations of individual Twitters users and selected 10-km as the cell size, which is the distinct geographic distance for separating two main groups of Twitter users in terms of their spatial coverage at the national level.
In addition, this choice enables us to focus on the inter-connections among different urban regions with less attention to movements around a user's neighborhood (i.e., within 10 km radius), such as home or work places.
The probability distributions of the radius of gyration for Twitter users in the Great Britain are verified to be consistent across different monthly time span, (see Supplement Materials section 1), which indicates the stability of using such measurements in this study.
It is worth noting that using

@@

The power of using Twitter user mobility to delineate non-administrative anthropographic boundaries is the ability to redraw the city at different mobility ranges inferred objectively from the collective mobility patterns. 
Urban boundaries redrawn based on Twitter user movement represent physical commutes rather than social ties or phone call initiation to reflect the human interaction space.
This study provides a first step in connecting human mobility research with defining non-administrative anthropographic boundaries, which could assist in resource allocation, political campaigns and urban planning.
